\documentclass[letterpaper,10pt]{amsart}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}
\hypersetup{colorlinks,breaklinks, urlcolor=Blue, linkcolor=Blue}
\urlstyle{same}
\usepackage{paralist}

%\renewcommand{\baselinestretch}{1.0}
%\renewcommand{\arraystretch}{1.1}

\newcommand{\resource}{\textsc}

\usepackage[charter]{mathdesign}
\usepackage{XCharter}

\title{Math 8000 Graduate Algebra, Fall 2017 --- Syllabus}
\author{Instructor: Asilata Bapat}
%\date{Fall 2017}

\begin{document}
\maketitle

\section{Outline of topics}
Groups and rings, including Sylow theorems, classifying small groups, finitely generated abelian groups, Jordan-Holder theorem, solvable groups, simplicity of the alternating group, euclidean domains, principal ideal domains, unique factorization domains, noetherian rings, Hilbert basis theorem, Zorn's lemma, and existence of maximal ideals and vector space bases.

\section{Resources}
My office is Boyd 605 and email is \url{asilata@uga.edu}.
The class meets every Tuesday and Thursday from \textbf{11:00am} to \textbf{12:15am} in \textbf{Boyd 326}.
Our textbook is \resource{Basic Algebra I, Nathan Jacobson}.
Additionally, there will be a problem session once every week.
Office hours will be announced later.

\textbf{Come to office hours!! I can't stress this enough.}
Come even if you don't have a specific question to ask, or are unsure what to ask.
If you have a question outside of office hours, post your question on \resource{piazza} (see below).
And if you're not sure whether or not you should ask a question, you should probably ask it.
There is a good chance that several your classmates are as unsure as you are, if not more so.

We have access to the following online resources.
\begin{compactenum}[(1)]
\item The website for the course is \url{https://asilata.github.io/8000fall17}, also accessible from my homepage.
  Check this often for updates, announcements, and homework.
\item This semester we will use \resource{piazza} for class discussion.
  I encourage you to post lots of questions on \resource{piazza}, so that you can get answers quickly from me as well as your fellow classmates.
  I hope this will also be a good resource leading up to your algebra qualifying exam.
  Our class page is \url{https://piazza.com/uga/fall2017/math8000/home}. 
  Check this often!
\item We have a class page on \resource{elc}, and your grades will be posted there.
\end{compactenum}

\section{Homework, Exams, Grading etc}
There will be (roughly) weekly homework.
There will also be two midterm exams and a final exam.
Dates and details will be announced later.
Additionally, you are expected to take turns taking notes of the lectures (``scribing''), and typing them up in \LaTeX.
This way we will have complete course notes at the end of the class, that you can refer to later.
Finally, you will be expected to take turns presenting homework solutions in the problem session.
Details about scribing and presentations will be announced in class.

The final grade will be calculated roughly according to the following distribution.
\begin{center}
  \begin{tabular}[t]{rl}
    40\%  & Homework\\
    30\%  & Two midterm exams (15\% per exam) \\
    20\%  & Final exam \\
    10\%  & Scribing and presentations \\
  \end{tabular}
\end{center}

\section{Collaboration policy}
You are allowed to (and encouraged to) collaborate on discussing the homework sets.
However, you must write up solutions entirely on your own.
This means in particular that you may not copy someone else's written work, copy/take pictures of the blackboard on which a solution has been written up, or write up solutions that you have looked up from the internet.
\textbf{Just to reiterate: if you are stuck, come to office hours, or post your question on \resource{piazza}}.
\end{document}
